Bootstrap Confidence Intervals for Sharp Regression Discontinuity Designs

### 2016-08-24 main_paper.tex
[#21] Make small adjustments to discussion of e_i^*
This commit corrects a grammar error and adds discussion of e_i^* to
the empirical section as well as the simulation section. People often
skip the simulations :)

To estimate the finite-sample coverage of our new bootstrap based confidence interval, we
simulate 5000 samples from each of the three DGPs (with $\gamma = 0$ and $\gamma = 2$) and calculate nominal 95\%
two-sided confidence intervals. We use 999 bootstrap replications ($B_2$) to
calculate the asymptotic distribution of the bias corrected estimator, and each
of those replications uses an additional 500 replications ($B_1$) to estimate
the bias. The bandwidths, $h$ and $b$,
are chosen using the AMSE-optimal rule proposed by CCT and the wild bootstrap
uses the ``HC3'' transformation of \citet{DF08}, defined in Equations~\eqref{eq:14}
and~\eqref{eq:15}. In our simulation studies as well as the application in the next section, we adopt two-point distribution for the $e_i^*$ when estimating our bootstrap procedure, i.e., $e_i^*$ equals $\frac{1 + \sqrt{5}}{2}$ with probability $ p = \frac{\sqrt{5} - 1}{2 \sqrt{5}}$ and $\frac{1 - \sqrt{5}}{2}$ with probability $1 - p$.

>>>>

To estimate the finite-sample coverage of our new bootstrap based confidence interval, we
simulate 5000 samples from each of the three DGPs (with $\gamma = 0$ and $\gamma = 2$) and calculate nominal 95\%
two-sided confidence intervals. We use 999 bootstrap replications ($B_2$) to
calculate the asymptotic distribution of the bias corrected estimator, and each
of those replications uses an additional 500 replications ($B_1$) to estimate
the bias. The bandwidths, $h$ and $b$,
are chosen using the AMSE-optimal rule proposed by CCT and the wild bootstrap
uses the ``HC3'' transformation of \citet{DF08}, defined in Equations~\eqref{eq:14}
and~\eqref{eq:15}. In these simulations, we use Mammen's (1993) \nocite{Mam93}
two-point distribution for $e_i^*$ in the bootstrap:
\begin{equation}
  \label{eq:19}
  e_i^* =
  \begin{cases}
    \frac{1 + \sqrt{5}}{2} & \text{with probability\ } \frac{\sqrt{5} - 1}{2 \sqrt{5}} \\
    \frac{1 - \sqrt{5}}{2} & \text{otherwise}.
  \end{cases}
\end{equation}
